---
title : "StreamPort python-to-r migration"
output : html_document
---

FIX PATH ID


Import reticulate to enable using python objects in R. py_run_string() statement here prints the current paths in the environment.

```{r setup, include=FALSE}
library(reticulate)
```



Adding current path to package so that related modules can be imported while handling relative imports.

```{python}
import os
import sys
sys.path.insert(0, os.path.abspath(os.getcwd()))
```

```{r}
py_run_string("print(sys.path)")
```



Import python modules to be run in R environment. Can be done using source_python().

```{r}
reticulate::source_python('C:\\Users\\PC0118\\Desktop\\StreamPort\\src\\StreamPort\\device\\DeviceEngine.py')
reticulate::source_python('C:\\Users\\PC0118\\Desktop\\StreamPort\\src\\StreamPort\\ml\\MachineLearningEngine.py')
```

```{r}
ml <- py$MachineLearningEngine()
ml$print()

```


```{r echo=FALSE}
dev <- py$DeviceEngine(source = r'(C:\Users\PC0118\Desktop\ExtractedSignals)')
analyses <- dev$find_analyses()
dev$add_analyses(analyses)
dev$print()
```


Can also be done by running python chunks. 

<!-- ```{python} -->
<!-- from src.StreamPort.device.DeviceEngine import DeviceEngine -->
<!-- from src.StreamPort.device.DeviceAnalysis import DeviceAnalysis -->
<!-- dev1 = DeviceEngine(source = r'C:\Users\PC0118\Desktop\ExtractedSignals') -->
<!-- dev1.print() -->
<!-- ``` -->

<!-- Now we can use the functions that belong to reticulate's python object 'py' -->

<!-- ```{r echo=FALSE} -->
<!-- analyses <- py$dev1$find_analyses() -->
<!-- py$dev1$add_analyses(analyses) -->
<!-- py$dev1$print() -->
<!-- ``` -->

Plot analyses

```{r}
dev$plot_analyses(group_by = 'date')
```

Extract features

<!-- ```{python} -->
<!-- from src.StreamPort.device.DeviceProcSettings import ExtractPressureFeatures -->
<!-- ``` -->

```{r}
source_python('C:\\Users\\PC0118\\Desktop\\StreamPort\\src\\StreamPort\\device\\DeviceProcSettings.py')
settings <- py$ExtractPressureFeatures(weighted = FALSE)
dev$add_settings(settings)
dev$print()
pressure_features <- settings$run(dev)
dev$add_results(pressure_features)
```

Seasonal Decomposition for signal component analysis

<!-- ```{python} -->
<!-- from src.StreamPort.device.DeviceProcSettings import DecomposeCurves -->
<!-- ``` -->
Problem here with conversion
```{r}
curve_decomposer <- py$DecomposeCurves(period = 30)
dev$add_settings(curve_decomposer)
components <- curve_decomposer$run(dev)
dev$add_results(components)
dev$get_results(-1)
```

Fourier transformation for visual identification of outlying frequencies

<!-- ```{python} -->
<!-- from src.StreamPort.device.DeviceProcSettings import FourierTransform -->
<!-- ``` -->

```{r}
fft <- py$FourierTransform()
dev$add_settings(fft)
dev$print()
transformed <- fft$run(dev)
dev$add_results(transformed)
```

Add features engineered from DecomposeCurves and FourierTransform to features matrix and scale them as a final preprocessing step before ML operations. Scaler from ProcessingSettings does the above mentioned preparation and scaling.

<!-- ```{python} -->
<!-- from src.StreamPort.device.DeviceProcSettings import Scaler -->
<!-- ``` -->

scaler options are 'minmax', 'std', 'robust', 'maxabs', 'norm' to be specified in 'parameters' argument.

```{r}
scaler <- py$Scaler(parameters = 'std')
dev$add_settings(scaler)
dev$print()
scaled <- scaler$run(dev)
dev$add_results(scaled)
```

Plot results

```{r}
methods <- dev$trim_method_name()
dev$plot_results(methods[1], features = 'base')
```
